---
title: "Bob Ross Tidy Tuesday Analysis"
output: html_notebook
---

```{r}
library(tidyverse)
library(cluster)
library(broom)
```

# Clustering Bob Ross's paining elements using MONothetic Analysis Clustering of Binary Variables

# Data Import, Cleaning, and Formatting
```{r}
bob_ross <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-08-06/bob-ross.csv")
```

```{r}
elements <- bob_ross %>%
  select(-EPISODE, -TITLE) %>%
  # there's one element, 'lakes', that only 1 is observed -
  # apparently there's a lake in every paining.
  # this causes an error when using mona, so make sure each column is a factor
  # with both 0 and 1 accounted for.
  mutate_all(.funs = factor, levels = c(0, 1)) 


```

# Clustering using MONothetic Analysis Clustering of Binary Variables
```{r}
elements_cluster <- mona(elements)
```

The mona clustering returns 10 clusters. 

```{r}
table(element_cluster$clustering)
```

Unfortunately I don't think the broom library can extract the model data produced by the mona clustering.
```{r}
broom::tidy(element_cluster)
```

```{r}
names(element_cluster)
```

# Visualization

Let's take a look at how some of the elements, currently stored as column names, occur within these clusters. 

```{r}
bob_ross$cluster = element_cluster$clustering

element_occurrence_tidy <- bob_ross %>%
  gather(element, occurrence, -EPISODE, -TITLE, -cluster) %>%
  filter(occurrence == 1) %>%
  mutate(cluster = as.factor(cluster))

element_occurrence_count <- element_occurrence_tidy %>%
  group_by(cluster, element) %>%
  tally() %>%
  arrange(desc(cluster), desc(n))

element_occurrence_count %>%
  group_by(cluster) %>%
  top_n(5, n) %>%
  ggplot(aes(x = fct_reorder(element, n), y = n, fill = cluster)) + 
  geom_bar(stat = "identity") +
  facet_wrap(~cluster, scales = "free", ncol = 2) +
  coord_flip()
```

```{r}
clusplot(elements, element_cluster$clustering, main = 'Cusplot')
```

